Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
HC -> hypercoercion

\figref{fig:HC-D} defines the constructors of \lazyD{} HC.

@@

The correctness proof of \lazyD\ HC is deferred to \secref{sec:LDHC-correct} 
because it relies on the space-efficient CEK abstract machine in 
\secref{sec:CEKS}.

>>>>

\figref{fig:HC-D} defines the constructors of \lazyD{} hypercoercion.

@@

The correctness proof of \lazyD\ hypercoercion is deferred to 
\secref{sec:LDHC-correct} 
because it relies on the space-efficient CEK abstract machine in 
\secref{sec:CEKS}.
